Usage metrics

### 2020-12-16 analysis/usage.Rmd
Plot explo
usage

```{r exercised-call-site-per-variant}
static_eval <- P %>% filter(call_fun_name == "eval") %>% nrow()
static_evalq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
static_eval.parent <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
static_local <- P %>% filter(call_fun_name == "local") %>% nrow()

sites_per_variant <- E %>% # src_ref indicates where the call originates from.
  group_by(ev_variant) %>% 
  summarize( n = n_distinct(src_ref)) # This the number of distinct sites

trig_eval <- sites_per_variant %>% filter(ev_variant == "eval")
trig_eval <- if(nrow(trig_eval) == 0)
{
  0
} else
{
  trig_eval$n
}

trig_evalq <- sites_per_variant %>% filter(ev_variant == "evalq")
trig_evalq <- if(nrow(trig_evalq) == 0)
{
  0
} else
{
  trig_evalq$n
}
trig_eval.parent <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
trig_eval.parent <- if(nrow(trig_eval.parent) == 0)
{
  0
} else
{
  trig_eval.parent$n
}
trig_local <- sites_per_variant %>% filter(ev_variant == "local")
trig_local <- if(nrow(trig_local) == 0)
{
  0
} else
{
  trig_local$n
}

overview_table(
  r("StaticEval", static_eval),
  r("StaticEvalq", static_evalq),
  r("StaticEvalParent", static_eval.parent),
  r("StaticLocal", static_local),
  r("TriggeredEval", trig_eval),
  r("TriggeredEvalq", trig_evalq),
  r("Triggeredevalparent", trig_eval.parent),
  r("Triggeredlocal", trig_local),
  r("Triggeredevalpercent", ratio(trig_eval, static_eval)),
  r("Triggeredevalqpercent", ratio(trig_evalq, static_evalq)),
  r("Triggeredevalparentpercent", ratio(trig_eval.parent, static_eval.parent)),
  r("Triggeredlocalpercent", ratio(trig_local, static_local))
) -> TBL
```

>>>>

# Exercised vs. Static

```{r exercised-vs-static, include=FALSE}
stat_evl <- P %>% filter(call_fun_name == "eval") %>% nrow()
stat_evq <- P %>% filter(call_fun_name == "evalq") %>% nrow()
stat_evp <- P %>% filter(call_fun_name == "eval.parent") %>% nrow()
stat_loc <- P %>% filter(call_fun_name == "local") %>% nrow()

sites_per_variant <- E %>% # src_ref indicates where the call originates from.
  group_by(ev_variant) %>%
  summarize(n = n_distinct(src_ref)) # This the number of distinct sites

tmp <- sites_per_variant %>% filter(ev_variant == "eval")
dyn_evl <- if (nrow(tmp)==0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "evalq")
dyn_evq <- if (nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
dyn_evalp <- if(nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "local")
dyn_lol <- if(nrow(tmp) == 0) { 0 } else { tmp$n }

overview_table(
  r("Staticeval", stat_evl),
  r("Staticevalq", stat_evq),
  r("Staticevalparent", stat_evp),
  r("Staticlocal", stat_loc),
  r("Triggeredeval", dyn_evl),
  r("Triggeredevalq", dyn_evq),
  r("Triggeredevalparent", dyn_evp),
  r("Triggeredlocal", dyn_loc),
  r("Triggeredevalpct", ratio(dyn_evl, stat_evl)),
  r("Triggeredevalqpct", ratio(dyn_evq, stat_evq)),
  r("Triggeredevalparentpct", ratio(dyn_evp, stat_evp)),
  r("Triggeredlocalpct", ratio(dyn_loc, stat_loc))
) -> TBL
```
